Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
ish fin conclusion p

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology and we introduce concepts of scale within the existing multilayer 
framework. Silk et al. (2018) summarized some 
key multilayer questions in animal behaviour
research  and based on our case study of scale in the context of multilayer 
networks, we conclude by posing an additional set of questions on the future 
of multilayer networks through the lens of scale and behavioural, landscape, 
and spatial ecology:

@@

We show that (1) multilayer social networks are scale-dependent, and (2) the use
of multilayer networks is useful for identifying spatially or temporally
specific social associations. It is important to consider a broad continuum of
scales to fully capture ecological processes, carefully select and combine data
with different temporal and spatial scales, and establish a clear link between
biologically relevant scales of observation.

<!-- TODO: round it out -->

<!-- conclusion -->

>>>>

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology and we introduce concepts of scale within the existing multilayer
framework. Silk et al. [-@Silk_2018] summarized some key multilayer questions in animal
behaviour research  and based on our case study of scale in the context of
multilayer networks, we conclude by posing an additional set of questions on the
future of multilayer networks through the lens of scale and behavioural,
landscape, and spatial ecology:

@@

We show that multilayer social networks are (1) scale-dependent, and (2) useful
for identifying spatially or temporally specific social associations. When
employing multilayer networks, it is important to consider a broad continuum of
social, spatial and temporal scales to fully capture ecological processes and
establish a clear link between biologically relevant scales of observation.
<!-- conclusion -->
